---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# CaseWeightLasso

## Overview

CaseWeightLasso focuses on the Case-weight Adjusted Lasso Model: 

$$
min_{\beta_0,\mathbf{\beta}}\quad \frac{1}{2}\sum_{i\neq k} (y_i - \beta_0 - \mathbf{x}_i^\top\mathbf{\beta})^2 + \frac{1}{2}\omega(y_k - \beta_0 - \mathbf{x}_k^\top\mathbf{\beta})^2 +\lambda \sum_{j=1}^p |\beta_j|
$$

The main utility of this package is the solution path algorithm and calculating the exact Cook's distance for the Lasso for observations of interest. The details can be found in []. This package is built based on [lars](https://cran.r-project.org/web/packages/lars/index.html) package by Hastie et al and require [tidyverse](https://www.tidyverse.org/) and [latex2exp](https://cran.r-project.org/web/packages/latex2exp/index.html) as prerequisites.

## Installation

You can install from CRAN with:

```R
install.packages("CaseWeightLasso")
```

You can also install the development version from GitHub using [devtools](http://cran.r-project.org/web/packages/devtools/index.html):
```{r, eval=FALSE}
devtools::install_github('zbjiao/CaseWeightLasso')
```

## Usage

```{r}
library(CaseWeightLasso, quietly = T)
```

We use synthetic data to demonstrate the usage of this package. Consider X has $n=50$, $p=200$. Only the first 5 predictors are informative. 

$$
y = 5x_1+4x_2+3x_3+2x_4+x_5 + e,\ e\sim N(0,1).
$$

```{r}
set.seed(100)
x = matrix(rnorm(50*200),nrow=50)
y = x[,1:5]%*%c(5,4,3,2,1) + rnorm(50)
```

### Leave-one-out Solution Path 

Suppose we are interested in observation 1's influence on the model at fraction = 0.7:
```{r}
obj = SolPathLooLasso(x,y,k = 1, s = 0.7, mode = "fraction")
```

`obj' is a SolPathLooLasso object that records the path of different statistics as $\omega$ decreases from 1 to 0. We can plot solution path (only coefficients that have sign change are included in the figure),
```{r}
plot(obj)
```

output the leave-one-out estimate of $y$ given a new set of $x$,
```{r}
predict(obj,t(rnorm(200)),'fit')
```
or simply output the leave-one-out estimate of coefficients.
```{r}
coef(obj)[2:12,]
```

### Cook's distance for the Lasso 

Another part of this package is calculating and visualizing Cook's distance for the Lasso. 

The option 'resid' gives you the residual-leverage plot.
```{r}
obj1 = CookDisLasso(x,y, k=1:10, s=c(0.1,0.2), mode = "fraction", threshold = FALSE)
plot(obj1, 'resid', 1)
```

The option 'case-influence-graph' gives you the case influence graph where you can see how case influence for the Lasso of each samples change as penalty level increases. 
```{r}
obj2 = CookDisLasso(x,y, fineness=40, threshold = TRUE)
plot(obj2, 'case-influence-graph')
```



